The Heavy Photon Search Test Detector

### 2014-04-23 hps-testrun-nim.tex
trying to fix table nr issue..no luck

\subsection{Trigger Rate Comparisons}
\label{sec:mcs}
Trigger rates observed in the HPS Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
distribution and the subsequent multiple Coulomb scattering in the converter. Rates from different 
converter 
thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
angle is constant). 
%\begin{center}
\begin{table}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted event rate (in Hz) normalized to 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
}
\label{tab:results}
\end{table}
%\end{center}
Restricting clusters to a well calibrated region of the ECal and subtracting the ``no converter'' 
background we see agreement with the rates predicted by the \egs{} simulation 
program, see Table~\ref{tab:results}.
This gives further confidence that the dominant source of background occupancy for HPS, multiple 
Coulomb scattered beam electrons, is well 
described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
%One of the main goals of the HPS Test Run was to evaluate the description of the tails of the 
%multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
%experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
%whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
%for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
%Despite all data taken with a photon beam in the HPS Test Run,

>>>>

\subsection{Trigger Rate Comparisons}
Trigger rates observed in the HPS Test Run are dominated by multiple Coulomb scattered \ee{} pairs in the 
converter. In simulated events, the rate of triggers depend on the modeling of the pairs angular 
distribution and the subsequent multiple Coulomb scattering in the converter. Rates from different 
converter 
thicknesses are used to study the varying multiple Coulomb scattering contribution (pair production 
angle is constant). 
%\begin{center}
\begin{table}
\label{results}
{\small
\begin{tabular}{|l|c|c|c|}
\hline
\bf Converter (\%~$X_0$) & \bf 1.60 & \bf 0.45 &	\bf 0.18 \\
\hline
EGS5 &	1162 $\pm$ 112 &	255 $\pm$ 28 &	94 $\pm$ 17	\\
\hline
GEANT4 & 2633 $\pm$ 250 & 	371 $\pm$ 38 &	114 $\pm$ 18 \\
\hline
Observed 	& 1064 $\pm$ 2 & 196 $\pm$ 1 &	92 $\pm$ 1 \\						
\hline
\end{tabular}
\caption{ Observed and predicted event rate (in Hz) normalized to 90~nA for three different converter 
thicknesses. The uncertainty on the prediction includes systematic uncertainties from ECal alignment, background normalization, beam current normalization and limited statistics in the simulation.}
}
\end{table}
%\end{center}
Restricting clusters to a well calibrated region of the ECal and subtracting the ``no converter'' 
background we see agreement with the rates predicted by the \egs{} simulation 
program, 
see Table~\ref{results}.
This gives further confidence that the dominant source of background occupancy for HPS, multiple 
Coulomb scattered beam electrons, is well 
described~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467} . 
%One of the main goals of the HPS Test Run was to evaluate the description of the tails of the 
%multiple Coulomb scattering to gain further confidence in the expected detector occupancy in the full HPS 
%experiment. Those occupancies have been evaluated using \egs{}~\cite{egs5} simulation program 
%whose \moliere{} formulation of multiple scattering show good agreement with previous studies 
%for a wide range of materials and projectiles~\cite{Attwood:2005zz,Shen:1978ha,Gottschalk1993467}. 
%Despite all data taken with a photon beam in the HPS Test Run,
